---
title: "CKME136-Text_Classification_&_Sentiment_Analysis"
author: Ian Santillan
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Text Classification & Sentiment Analysis

Text analytics is the process of analyzing unstructured text, extracting relevant information, and transforming it into useful business intelligence.

Sentiment analysis determines if an expression is positive, negative, or neutral, and to what degree.

In other words, text analytics studies the face value of the words, including the grammar and the relationships among the words. Simply put, text analytics gives you the meaning. Sentiment analysis gives you insight into the emotion behind the words.


For this project, I will be analyzing Stantec's public tweets, https://twitter.com/stantec.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
