---
title: "CKME136-Text_Classification_&_Sentiment_Analysis"
author: Ian Santillan
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Text Classification & Sentiment Analysis

Text analytics is the process of analyzing unstructured text, extracting relevant information, and transforming it into useful business intelligence.

Sentiment analysis determines if an expression is positive, negative, or neutral, and to what degree.

In other words, text analytics studies the face value of the words, including the grammar and the relationships among the words. Simply put, text analytics gives you the meaning. Sentiment analysis gives you insight into the emotion behind the words.


For this project, I will be analyzing Stantec's public tweets, https://twitter.com/stantec.

```{r packages}
#load the required packages
install.packages(c("twitteR", "ROAuth", "plyr", "stringr", "ggplot2"), dependencies = TRUE)


library(twitteR)
library(ROAuth)
library(plyr)
library(stringr)
library(ggplot2)


# need to download this file for Windows
download.file(url = "http://curl.haxx.se/ca/cacert.pem", destfile = "cacert.pem")

```

## Twitter API

Get the Twitter application information from https://apps.twitter.com/app/15285185 

Application Settings

Consumer Key (API Key) - 23N7OF29dGUuZ3n7yJG9vEhbV
Consumer Secret (API Secret) - 4CuzRmbsPnqy2fHf8XgPVaxoZjpq0hKLtEK5wKtAeTq8Jm36rk
Access Level	- Read and write
Owner	- eye_an
Owner ID	- 23886393
Callback URL -	None
Callback URL Locked -	Yes
Sign in with Twitter -	Yes
App-only authentication -	https://api.twitter.com/oauth2/token
Request token URL -	https://api.twitter.com/oauth/request_token
Authorize URL -	https://api.twitter.com/oauth/authorize
Access token URL -	https://api.twitter.com/oauth/access_token


```{r Twitter API}

# accessing the Twitter API

requestURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "https://api.twitter.com/oauth/access_token"
authURL <- "https://api.twitter.com/oauth/authorize"
consumerKey <- "23N7OF29dGUuZ3n7yJG9vEhbV"
consumerSecret <- "4CuzRmbsPnqy2fHf8XgPVaxoZjpq0hKLtEK5wKtAeTq8Jm36rk"
Cred <- OAuthFactory$new(consumerKey = consumerKey,
                         consumerSecret = consumerSecret,
                         requestURL = requestURL, 
                         accessURL = accessURL,
                         authURL = authURL)
Cred$handshake(cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
